### 2019-01-04 manuscript/manuscript.rmd
added parallel code

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)
library(ape)
library(igraph)

source( "functions.R" )
```

@@

sequence_matrices = lapply(
	phylip_file_names,
	function( phylip_file ){
		print(phylip_file)
		partition_file = sub( "phy$", "nex", phylip_file )

@@

		return( sequence_matrix )
	}
)

@@

trees = lapply(
	tree_file_names,
	function( tree_file ){
		print(tree_file)
		log_file = sub( str_c( contree_extension, "$" ), "log", tree_file )

@@

		if(!file.exists(log_file_path)){
			warning( str_c( "Missong log file: ", log_file_path ) )
			return( NA )
		}

@@

@@

		# Stuff a few other things into the tree object
		tree$matrix = matrix_name
		tree$model = model_name
		tree$modelfinder = FALSE
		tree$clades = clades
		tree$sampling = sampling

@@

		return( tree )
	}
)

>>>>

```{r preliminaries}
library( tidyverse )
library( magrittr )
library(viridis)
library(ape)
library(igraph)
library(hutan)
library(doParallel)

source( "functions.R" )

# Set system computational parameters
cores = detectCores() - 1
if ( cores < 1 ) {
	cores = 1
}

# Register parallel workers for %dopar%
registerDoParallel( cores )
```

@@

parse_phylip =	function( phylip_file ){
		print(phylip_file)
		partition_file = sub( "phy$", "nex", phylip_file )

@@

		return( sequence_matrix )
	}

sequence_matrices = foreach( phylip_file=phylip_file_names) %dopar%
	parse_phylip( phylip_file )

@@

# Temp fix re issue #8
tree_file_names = tree_file_names[ ! grepl("Philippe2009", tree_file_names) ]

tree_file_names = tree_file_names[ ! grepl("Nosenko2013", tree_file_names) ]

parse_tree = 	function( tree_file ){
		print(tree_file)
		log_file = sub( str_c( contree_extension, "$" ), "log", tree_file )
		bootstrap_file = sub( str_c( contree_extension, "$" ), "ufboot", tree_file )

@@

		if(!file.exists(log_file_path)){
			warning( str_c( "Missing log file: ", log_file_path ) )
			return( NA )
		}

		bootstrap_file_path = paste(c(trees_path, bootstrap_file), collapse="")
		if(!file.exists(bootstrap_file_path)){
			warning( str_c( "Missing bootstrap file: ", bootstrap_file_path ) )
			return( NA )
		}

@@

		if( is.na(outgroup) ){
			stop( "There are no outgroups in the tree, can't test rooting topology" )
		}

@@

		if( sum(is.na(clades)) > 0 ){
			missing_clades = tree$tip.label[ is.na(clades) ]
			stop( paste( c( "Some tips have missing clade names:", missing_clades ), collapse=" " ))
		}

		if( sum(clades == "Ctenophora") < 1 ){
			stop( "There are no ctenophores in the tree, can't test rooting topology" )
		}

		if( sum(clades == "Porifera") < 1 ){
			stop( "There are no sponges in the tree, can't test rooting topology" )
		}

		# Get the set of taxa in the group Ctenophora+Placozoa+Bilateria+Cnidaria, the clade that exists under Proifera-sister
		CtPlBiCn = tree$tip.label[ clades %in% c("Ctenophora", "Placozoa", "Bilateria", "Cnidaria") ]

		# Get the set of taxa in the group Porifera+Placozoa+Bilateria+Cnidaria, the clade that exists under Ctenophora-sister
		PoPlBiCn = tree$tip.label[ clades %in% c("Porifera", "Placozoa", "Bilateria", "Cnidaria") ]

		# Read the bootstrap trees
		bootstrap_trees = read.tree(file = bootstrap_file_path)

		Ctenophora_sister = lapply(
			bootstrap_trees,
			function( phy ){
				is_monophyletic( phy, PoPlBiCn )
			}
		) %>% 
		unlist() %>%
		mean()

		Porifera_sister = lapply(
			bootstrap_trees,
			function( phy ){
				is_monophyletic( phy, CtPlBiCn )
			}
		) %>% 
		unlist() %>%
		mean()

		# Stuff a few other things into the tree object
		tree$matrix = matrix_name
		tree$model = model_name
		tree$modelfinder = FALSE
		tree$clades = clades
		tree$sampling = sampling
		tree$ctenophora_sister = Ctenophora_sister
		tree$porifera_sister = Porifera_sister

@@

		return( tree )
	}

trees = foreach( tree_file=tree_file_names) %dopar%
	parse_tree( tree_file )
